---
title: "Simulate and analyze data for paper"
author: "Chris McKennan"
date: "10/29/2017"
output: html_document
---

Running this script will reproduce the simulation results presented in the paper. To run, make sure the packages under "Libraries" are installed. To install our software BCconf, type the following into R:

install.packages("devtools")
devtools::install_github("chrismckennan/BCconf/BCconf")


##Libraries
All libraries used in simulations
```{r Library}
library(cate)
library(parallel)
library(qvalue)
library(irlba)
library(minfi)
library(sva)
library(dSVA)
library(ruv)
library(BCconf)
```

##Source functions
Set your directory structure to load the following R-scripts:
```{r Source}
setwd("/Users/Chris/Desktop/Uchicago/Nicolae/GitWork/CellType/analysis")

source("../R/Simulations/Simulation_171029.R")
source("../R/Simulations/DetermineFDP.R")
```
The file Simulation_171029.R contains the function "SimulateData"" used to simulate data. DetermineFDP.R contains the function "AnalyzeData" used to analyze the results of all methods. Specifically, for each method we

1.) Obtain each method's estimate for C, which is one of the objects returned by BCconf, cate, dSVA, sva, RUV-2 and RUV-4.
2.) Use the estimate for C, C.hat, to estimate beta_1,...,beta_p with ordinary least squares using the design matrix [1 X C.hat]. This is done with the function "CalcPvalues" in DetermineFDP.R.
3.) Calculate the false discovery proportion at a nominal false discovery proportion using q-value. This is done with the function "CalcFDP" in DetermineFDP.R.


#Simulations for paper

##Simulation 1
pi.B = 0.95, Omega = (0 x 5, 0.5 x 5)

Simulate data with A = A_2 and the E(Fraction of elements of B = 0) = 0.95
```{r SetParameters1}
n <- 100     #Number of samples
p <- 10^5    #Number of genomic units
K <- 10      #Number of latent factors
frac.variance <- 0.5    #If this is 0.5, C explains 30% of the variability in X, on average
B.sigma <- 0.4   #The non-zero comonents of B are simulated as B_g ~ N(0, B.sigma^2)
pi.B <- 0.95     #Expected fraction of components of B that are 0
L.sigma <- 0.5   #Minimum standard deviation for simulated L_{gk}
n.sim <- 100     #Number of simulated datasets to analyze
K.try <- c(K, K+10)     #The K's to be used with BCconf

Info <- c(exp(seq(log((n-2)), 0, length=K))[1:(K/2)], exp(seq(log((n-2)/5), 0, length=K))[(K/2+1):K])   #Exptected eigenvalues lambda_1,...,lambda_K
Omega2 <- frac.variance*B.sigma^2/sum(Info[(K/2+1):K]/(n-2))/(1-frac.variance)

##Set Omega##
#Omega <- rep(sqrt(Omega2*2/K), K)
Omega <- c(rep(0, K/2), rep(sqrt(Omega2*2/K), K/2))    #The parameter "A" in simulation section from paper
q.points <- seq(0.05, 0.25, by=0.05)     #q-value thresholds to consider

##Plot parameters##
col.plot <- c("red", "blue", "black")
pch.plot <- c(1, 2, 4)
lty.plot <- c(2, 3, 4)
dx.plot <- 0.005
```


Simulated and analyze data. I will use a t-distribution with 4 degrees of freedom for the residuals. Run this code to simulate and analyze data with the above simulation setting.
```{r SimulateAnalyzeData1}
delta.L <- pmin((Info/(n-2)) / L.sigma^2, 1)
out.mine <- array(0, dim=c(length(K.try), length(q.points), n.sim))    #FDP for BCconf
out.none <- matrix(0, nrow=length(q.points), ncol=n.sim)      #FDP for no correction
out.cate <- matrix(0, nrow=length(q.points), ncol=n.sim)      #FDP for CATE-RR
out.known <- matrix(0, nrow=length(q.points), ncol=n.sim)     #FDP when C is known
out.sva.irw <- matrix(0, nrow=length(q.points), ncol=n.sim)   #FDP for IRW-SVA
out.dsva <- matrix(0, nrow=length(q.points), ncol=n.sim)      #FDP for dSVA
out.ruv2 <- matrix(0, nrow=length(q.points), ncol=n.sim)      #FDP for RUV-2
out.ruv4 <- matrix(0, nrow=length(q.points), ncol=n.sim)      #FDP for RUV-4
out.power.mine <- array(0, dim=c(length(K.try), length(q.points), n.sim))      #Power for BCconf
out.power.known <- matrix(0, nrow=length(q.points), ncol=n.sim)      #Power when C is known
out.PecVar <- matrix(0, nrow=8, ncol=n.sim)  #Fraction of the variance in X explained by C
for (i in 1:n.sim) {
  Simulation <- SimulateData(n=n, p=p, Info=Info, Omega=Omega, L.sd=L.sigma, B.sd=B.sigma, B.pi=pi.B, mean.Sigma=1, var.Sigma=0.5^2, t.df=4)
  out <- AnalyzeData(Sim = Simulation, q.points = q.points, K.try=K.try, n.controls = 600)
  out.PecVar[,i] <- c(out$PercVar, out$PercVar.my[1], out$PercVar.my[2], out$PercVar.cate, out$PercVar.dsva, out$PercVar.sva, out$PercVar.ruv2, out$PercVar.ruv4)
  out.none[,i] <- out$FDP.none
  out.mine[,,i] <- out$FDP.my
  out.cate[,i] <- out$FDP.cate
  out.known[,i] <- out$FDP.known
  out.sva.irw[,i] <- out$FDP.sva.irw
  out.dsva[,i] <- out$FDP.dsva
  out.ruv4[,i] <- out$FDP.ruv4
  out.ruv2[,i] <- out$FDP.ruv2
  
  out.power.mine[,,i] <- out$Power.my
  out.power.known[,i] <- out$Power.known
  cat(i, "\n")
}
```

Plot results from above simulation
```{r PlotData1}
###Collate results###
n.points <- length(q.points)
my.results <- array(0, dim=c(2,3,n.points)); my.results[1,,] <- apply(out.mine[1,,], 1, function(x){quantile(x[x>0],c(0.25,0.5,0.75))}); my.results[2,,] <- apply(out.mine[2,,], 1, function(x){quantile(x[x>0],c(0.25,0.5,0.75))})
my.results.power <- array(0, dim=c(2,3,n.points)); my.results.power[1,,] <- apply(out.power.mine[1,,], 1, function(x){quantile(x[x>0],c(0.25,0.5,0.75))}); my.results.power[2,,] <- apply(out.power.mine[2,,], 1, function(x){quantile(x[x>0],c(0.25,0.5,0.75))})
known.power <- apply(out.power.known, 1, function(x){quantile(x[x > 0],c(0.25,0.5,0.75))})

cate.results <- apply(out.cate, 1, function(x){quantile(x[x > 0],c(0.25,0.5,0.75))})
dsva.results <- apply(out.dsva, 1, function(x){quantile(x[x > 0],c(0.25,0.5,0.75))})
sva.results <- apply(out.sva.irw, 1, function(x){quantile(x[x > 0],c(0.25,0.5,0.75))})
known.results <- apply(out.known, 1, function(x){quantile(x[x > 0],c(0.25,0.5,0.75))})
none.results <- apply(out.none, 1, function(x){quantile(x[x > 0],c(0.25,0.5,0.75))})
ruv2.results <- apply(out.ruv2, 1, function(x){quantile(x[x > 0],c(0.25,0.5,0.75))})
ruv4.results <- apply(out.ruv4, 1, function(x){quantile(x[x > 0],c(0.25,0.5,0.75))})

##Box plot of Results at a 20% FDR##
q.plot <- 0.2
axis.labels <- c("C known", expression(paste("BC, ", hat(K)==10)), expression(paste("BC, ", hat(K)==20)), "CATE-RR", "dSVA", "IRW-SVA", "RUV-2", "RUV-4", "None")

ind.plot <- which(q.points == q.plot)
data.plot <- data.frame(known = out.known[ind.plot,], my.10 = out.mine[1,ind.plot,], my.20 = out.mine[2,ind.plot,], cate=out.cate[ind.plot,], dsva=out.dsva[ind.plot,], sva=out.sva.irw[ind.plot,], ruv2=out.ruv2[ind.plot,], ruv4=out.ruv4[ind.plot,], none=out.none[ind.plot,])
boxplot(data.plot, axes=F, at=1:length(axis.labels), ylim=c(0,1))
axis(side = 2, at = seq(0,1,by=0.2))
axis(side = 1, at = 1:length(axis.labels), labels = axis.labels, las = 2)
title(ylab = "True FDP")
abline(h=q.plot, lty=2, lwd=2, col="red")
```

##Simulation 2
pi.B = 0.80, Omega = (0 x 5, 0.5 x 5)

Simulate data with A = A_2 and the E(Fraction of elements of B = 0) = 0.80
```{r SetParameters2}
n <- 100
p <- 10^5
K <- 10
frac.variance <- 0.5
B.sigma <- 0.4
pi.B <- 0.80
L.sigma <- 0.5
n.sim <- 100
K.try <- c(K, K+10)

Info <- c(exp(seq(log((n-2)), 0, length=K))[1:(K/2)], exp(seq(log((n-2)/5), 0, length=K))[(K/2+1):K])
#Info <- exp(seq(log((n-2)), 0, length=K))   #n/p * L'L; n/5 for paper
Omega2 <- frac.variance*B.sigma^2/sum(Info[(K/2+1):K]/(n-2))/(1-frac.variance)

##Set Omega##
#Omega <- rep(sqrt(Omega2*2/K), K)
Omega <- c(rep(0, K/2), rep(sqrt(Omega2*2/K), K/2))
q.points <- seq(0.05, 0.25, by=0.05)

##Plot Parameters##
col.plot <- c("red", "blue", "black")  #CATE, mine, known
pch.plot <- c(1, 2, 4)
lty.plot <- c(2, 3, 4)
dx.plot <- 0.005
```


Simulated and analyze data.
```{r SimulateAnalyzeData2}
delta.L <- pmin((Info/(n-2)) / L.sigma^2, 1)
out.mine <- array(0, dim=c(length(K.try), length(q.points), n.sim))
out.none <- matrix(0, nrow=length(q.points), ncol=n.sim)
out.cate <- matrix(0, nrow=length(q.points), ncol=n.sim)
out.known <- matrix(0, nrow=length(q.points), ncol=n.sim)
out.sva.irw <- matrix(0, nrow=length(q.points), ncol=n.sim)
out.dsva <- matrix(0, nrow=length(q.points), ncol=n.sim)
out.ruv2 <- matrix(0, nrow=length(q.points), ncol=n.sim)
out.ruv4 <- matrix(0, nrow=length(q.points), ncol=n.sim)
out.power.mine <- array(0, dim=c(length(K.try), length(q.points), n.sim))
out.power.known <- matrix(0, nrow=length(q.points), ncol=n.sim)
for (i in 1:n.sim) {
  Simulation <- SimulateData(n=n, p=p, Info=Info, Omega=Omega, L.sd=L.sigma, B.sd=B.sigma, B.pi=pi.B, mean.Sigma=1, var.Sigma=0.5^2, t.df=4)
  out <- AnalyzeData(Sim = Simulation, q.points = q.points, K.try=K.try, n.controls = 600)
  out.none[,i] <- out$FDP.none
  out.mine[,,i] <- out$FDP.my
  out.cate[,i] <- out$FDP.cate
  out.known[,i] <- out$FDP.known
  out.sva.irw[,i] <- out$FDP.sva.irw
  out.dsva[,i] <- out$FDP.dsva
  out.ruv4[,i] <- out$FDP.ruv4
  out.ruv2[,i] <- out$FDP.ruv2
  
  out.power.mine[,,i] <- out$Power.my
  out.power.known[,i] <- out$Power.known
  cat(i, "\n")
}
```


```{r PlotData2}
###Collate results###
n.points <- length(q.points)
my.results <- array(0, dim=c(2,3,n.points)); my.results[1,,] <- apply(out.mine[1,,], 1, function(x){quantile(x,c(0.25,0.5,0.75))}); my.results[2,,] <- apply(out.mine[2,,], 1, function(x){quantile(x,c(0.25,0.5,0.75))})
cate.results <- apply(out.cate, 1, function(x){quantile(x,c(0.25,0.5,0.75))})
dsva.results <- apply(out.dsva, 1, function(x){quantile(x,c(0.25,0.5,0.75))})
sva.results <- apply(out.sva.irw, 1, function(x){quantile(x,c(0.25,0.5,0.75))})
known.results <- apply(out.known, 1, function(x){quantile(x,c(0.25,0.5,0.75))})
none.results <- apply(out.none, 1, function(x){quantile(x,c(0.25,0.5,0.75))})
ruv2.results <- apply(out.ruv2, 1, function(x){quantile(x,c(0.25,0.5,0.75))})
ruv4.results <- apply(out.ruv4, 1, function(x){quantile(x,c(0.25,0.5,0.75))})


##Box plot of Results at a 20% FDR##
q.plot <- 0.2
axis.labels <- c("C known", expression(paste("BC, ", hat(K)==10)), expression(paste("BC, ", hat(K)==20)), "CATE-RR", "dSVA", "IRW-SVA", "RUV-2", "RUV-4", "None")

ind.plot <- which(q.points == q.plot)
data.plot <- data.frame(known = out.known[ind.plot,], my.10 = out.mine[1,ind.plot,], my.20 = out.mine[2,ind.plot,], cate=out.cate[ind.plot,], dsva=out.dsva[ind.plot,], sva=out.sva.irw[ind.plot,], ruv2=out.ruv2[ind.plot,], ruv4=out.ruv4[ind.plot,], none=out.none[ind.plot,])
boxplot(data.plot, axes=F, at=1:length(axis.labels), ylim=c(0,1))
axis(side = 2, at = seq(0,1,by=0.2))
axis(side = 1, at = 1:length(axis.labels), labels = axis.labels, las = 2)
title(ylab = "True FDP")
abline(h=q.plot, lty=2, lwd=2, col="red")
```

##Simulation 3
pi.B = 0.95, Omega = (0.5 x 5, 0 x 5)

Simulate data with A = A_1 and the E(Fraction of elements of B = 0) = 0.95
```{r SetParameters3}
n <- 100
p <- 10^5
K <- 10
frac.variance <- 0.5   
B.sigma <- 0.4  
pi.B <- 0.95
L.sigma <- 0.5
n.sim <- 100
K.try <- c(K, K+10)

Info <- c(exp(seq(log((n-2)), 0, length=K))[1:(K/2)], exp(seq(log((n-2)/5), 0, length=K))[(K/2+1):K])
#Info <- exp(seq(log((n-2)), 0, length=K))   #n/p * L'L; n/5 for paper
Omega2 <- frac.variance*B.sigma^2/sum(Info[(K/2+1):K]/(n-2))/(1-frac.variance)

##Set Omega##
#Omega <- rep(sqrt(Omega2*2/K), K)
Omega <- c(rep(sqrt(Omega2*2/K), K/2), rep(0, K/2))
q.points <- seq(0.05, 0.25, by=0.05)

##Plot Parameters##
col.plot <- c("red", "blue", "black")  #CATE, mine, known
pch.plot <- c(1, 2, 4)
lty.plot <- c(2, 3, 4)
dx.plot <- 0.005
```


Simulated and analyze data.
```{r SimulateAnalyzeData3}
delta.L <- pmin((Info/(n-2)) / L.sigma^2, 1)
out.mine <- array(0, dim=c(length(K.try), length(q.points), n.sim))
out.none <- matrix(0, nrow=length(q.points), ncol=n.sim)
out.cate <- matrix(0, nrow=length(q.points), ncol=n.sim)
out.known <- matrix(0, nrow=length(q.points), ncol=n.sim)
out.sva.irw <- matrix(0, nrow=length(q.points), ncol=n.sim)
out.dsva <- matrix(0, nrow=length(q.points), ncol=n.sim)
out.ruv2 <- matrix(0, nrow=length(q.points), ncol=n.sim)
out.ruv4 <- matrix(0, nrow=length(q.points), ncol=n.sim)
out.power.mine <- array(0, dim=c(length(K.try), length(q.points), n.sim))
out.power.known <- matrix(0, nrow=length(q.points), ncol=n.sim)
for (i in 1:n.sim) {
  Simulation <- SimulateData(n=n, p=p, Info=Info, Omega=Omega, L.sd=L.sigma, B.sd=B.sigma, B.pi=pi.B, mean.Sigma=1, var.Sigma=0.5^2, t.df=4)
  out <- AnalyzeData(Sim = Simulation, q.points = q.points, K.try=K.try, n.controls = 600)
  out.none[,i] <- out$FDP.none
  out.mine[,,i] <- out$FDP.my
  out.cate[,i] <- out$FDP.cate
  out.known[,i] <- out$FDP.known
  out.sva.irw[,i] <- out$FDP.sva.irw
  out.dsva[,i] <- out$FDP.dsva
  out.ruv4[,i] <- out$FDP.ruv4
  out.ruv2[,i] <- out$FDP.ruv2
  
  out.power.mine[,,i] <- out$Power.my
  out.power.known[,i] <- out$Power.known
  cat(i, "\n")
}
```

```{r PlotData3}
###Collate results###
n.points <- length(q.points)
my.results <- array(0, dim=c(2,3,n.points)); my.results[1,,] <- apply(out.mine[1,,], 1, function(x){quantile(x,c(0.25,0.5,0.75))}); my.results[2,,] <- apply(out.mine[2,,], 1, function(x){quantile(x,c(0.25,0.5,0.75))})
cate.results <- apply(out.cate, 1, function(x){quantile(x,c(0.25,0.5,0.75))})
dsva.results <- apply(out.dsva, 1, function(x){quantile(x,c(0.25,0.5,0.75))})
sva.results <- apply(out.sva.irw, 1, function(x){quantile(x,c(0.25,0.5,0.75))})
known.results <- apply(out.known, 1, function(x){quantile(x,c(0.25,0.5,0.75))})
none.results <- apply(out.none, 1, function(x){quantile(x,c(0.25,0.5,0.75))})
ruv2.results <- apply(out.ruv2, 1, function(x){quantile(x,c(0.25,0.5,0.75))})
ruv4.results <- apply(out.ruv4, 1, function(x){quantile(x,c(0.25,0.5,0.75))})

##Box plot of Results at a 20% FDR##
q.plot <- 0.2
axis.labels <- c("C known", expression(paste("BC, ", hat(K)==10)), expression(paste("BC, ", hat(K)==20)), "CATE-RR", "dSVA", "IRW-SVA", "RUV-2", "RUV-4", "None")

ind.plot <- which(q.points == q.plot)
data.plot <- data.frame(known = out.known[ind.plot,], my.10 = out.mine[1,ind.plot,], my.20 = out.mine[2,ind.plot,], cate=out.cate[ind.plot,], dsva=out.dsva[ind.plot,], sva=out.sva.irw[ind.plot,], ruv2=out.ruv2[ind.plot,], ruv4=out.ruv4[ind.plot,], none=out.none[ind.plot,])
boxplot(data.plot, axes=F, at=1:length(axis.labels), ylim=c(0,1))
axis(side = 2, at = seq(0,1,by=0.2))
axis(side = 1, at = 1:length(axis.labels), labels = axis.labels, las = 2)
title(ylab = "True FDP")
abline(h=q.plot, lty=2, lwd=2, col="red")
```

##Simulation 4
pi.B = 0.80, Omega = (0.5 x 5, 0 x 5)

Simulate data with A = A_1 and the E(Fraction of elements of B = 0) = 0.80
```{r SetParameters4}
n <- 100
p <- 10^5
K <- 10
frac.variance <- 0.5  
B.sigma <- 0.4   
pi.B <- 0.80
L.sigma <- 0.5
n.sim <- 100
K.try <- c(K, K+10)

Info <- c(exp(seq(log((n-2)), 0, length=K))[1:(K/2)], exp(seq(log((n-2)/5), 0, length=K))[(K/2+1):K])
#Info <- exp(seq(log((n-2)), 0, length=K))   #n/p * L'L; n/5 for paper
Omega2 <- frac.variance*B.sigma^2/sum(Info[(K/2+1):K]/(n-2))/(1-frac.variance)

##Set Omega##
#Omega <- rep(sqrt(Omega2*2/K), K)
Omega <- c(rep(sqrt(Omega2*2/K), K/2), rep(0, K/2))
q.points <- seq(0.05, 0.25, by=0.05)

##Plot Parameters##
col.plot <- c("red", "blue", "black")  #CATE, mine, known
pch.plot <- c(1, 2, 4)
lty.plot <- c(2, 3, 4)
dx.plot <- 0.005
```
With these values of Omega, C is explaining 30% of the variability in X, on average. Some things to note: CATE fails for obvious reasons. IRW SVA tends to fail when the confounding signal is large because the first step in the algorithm effectively looks for genes with small correlation with X, which will be very few genes i

Simulated and analyze data. I will use a t-distribution with 4 degrees of freedom; tmp.cate, tmp.mine
```{r SimulateAnalyzeData4}
delta.L <- pmin((Info/(n-2)) / L.sigma^2, 1)
out.mine <- array(0, dim=c(length(K.try), length(q.points), n.sim))
out.none <- matrix(0, nrow=length(q.points), ncol=n.sim)
out.cate <- matrix(0, nrow=length(q.points), ncol=n.sim)
out.known <- matrix(0, nrow=length(q.points), ncol=n.sim)
out.sva.irw <- matrix(0, nrow=length(q.points), ncol=n.sim)
out.dsva <- matrix(0, nrow=length(q.points), ncol=n.sim)
out.ruv2 <- matrix(0, nrow=length(q.points), ncol=n.sim)
out.ruv4 <- matrix(0, nrow=length(q.points), ncol=n.sim)
out.power.mine <- array(0, dim=c(length(K.try), length(q.points), n.sim))
out.power.known <- matrix(0, nrow=length(q.points), ncol=n.sim)
for (i in 1:n.sim) {
  Simulation <- SimulateData(n=n, p=p, Info=Info, Omega=Omega, L.sd=L.sigma, B.sd=B.sigma, B.pi=pi.B, mean.Sigma=1, var.Sigma=0.5^2, t.df=4)
  out <- AnalyzeData(Sim = Simulation, q.points = q.points, K.try=K.try, n.controls = 600)
  out.none[,i] <- out$FDP.none
  out.mine[,,i] <- out$FDP.my
  out.cate[,i] <- out$FDP.cate
  out.known[,i] <- out$FDP.known
  out.sva.irw[,i] <- out$FDP.sva.irw
  out.dsva[,i] <- out$FDP.dsva
  out.ruv4[,i] <- out$FDP.ruv4
  out.ruv2[,i] <- out$FDP.ruv2
  
  out.power.mine[,,i] <- out$Power.my
  out.power.known[,i] <- out$Power.known
  cat(i, "\n")
}
```

```{r PlotData4}
###Collate results###
n.points <- length(q.points)
my.results <- array(0, dim=c(2,3,n.points)); my.results[1,,] <- apply(out.mine[1,,], 1, function(x){quantile(x,c(0.25,0.5,0.75))}); my.results[2,,] <- apply(out.mine[2,,], 1, function(x){quantile(x,c(0.25,0.5,0.75))})
cate.results <- apply(out.cate, 1, function(x){quantile(x,c(0.25,0.5,0.75))})
dsva.results <- apply(out.dsva, 1, function(x){quantile(x,c(0.25,0.5,0.75))})
sva.results <- apply(out.sva.irw, 1, function(x){quantile(x,c(0.25,0.5,0.75))})
known.results <- apply(out.known, 1, function(x){quantile(x,c(0.25,0.5,0.75))})
none.results <- apply(out.none, 1, function(x){quantile(x,c(0.25,0.5,0.75))})
ruv2.results <- apply(out.ruv2, 1, function(x){quantile(x,c(0.25,0.5,0.75))})
ruv4.results <- apply(out.ruv4, 1, function(x){quantile(x,c(0.25,0.5,0.75))})

##Box plot of Results at a 20% FDR##
q.plot <- 0.2
axis.labels <- c("C known", expression(paste("BC, ", hat(K)==10)), expression(paste("BC, ", hat(K)==20)), "CATE-RR", "dSVA", "IRW-SVA", "RUV-2", "RUV-4", "None")

ind.plot <- which(q.points == q.plot)
data.plot <- data.frame(known = out.known[ind.plot,], my.10 = out.mine[1,ind.plot,], my.20 = out.mine[2,ind.plot,], cate=out.cate[ind.plot,], dsva=out.dsva[ind.plot,], sva=out.sva.irw[ind.plot,], ruv2=out.ruv2[ind.plot,], ruv4=out.ruv4[ind.plot,], none=out.none[ind.plot,])
boxplot(data.plot, axes=F, at=1:length(axis.labels), ylim=c(0,1))
axis(side = 2, at = seq(0,1,by=0.2))
axis(side = 1, at = 1:length(axis.labels), labels = axis.labels, las = 2)
title(ylab = "True FDP")
abline(h=q.plot, lty=2, lwd=2, col="red")
```

